Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors That Have Mixed During Cooling

### 2019-10-18 paper/reply_to_referee.txt

We thank the referee for reading our manuscript and offering very
constructive criticism and suggestions. We are in almost complete agreement
with the referee and have modified the manuscript accordingly. We address
our changes for each point below. As a result of our revisions, we believe 
the manuscript is stronger and we hope it is now ready for publication.

> *Methodology*

> - It is not clear to me if the input deflagration speed (pg 7) has been
> recalibrated to the particular initial composition of the mixed hybrid
> core. Willcox et al (2016) just reports recomputing detonations, but there
> is no mention of deflagrations (at least I have not been able to find it).

We regret not explaining the methodology of our deflagration speeds. The 
answer is that the deflagration speeds for input to the flame model are 
from tabulated results. Laminar flame speeds are first 
obtained by interpolation within a
three-dimensional table of 12C, 22Ne, and log density obtained from
prior direct numerical simulations. Here 22Ne is uses as a proxy for
for neutron-rich elements so the interpolated laminar flame speeds capture
the boost due to neutronization. These laminar flame speed are
then boosted to account for the effects of unresolved buoyancy
and background turbulence and passed to the flame model. We have
updated the text of section 2.1 to explain the flame speeds
and included a citation to earlier work describing the tabulated
flame speeds in detail.

@@

[AC NOTE: CHECK THE ABOVE. The models include 20Ne. Does the above
description properly account for that? As I recall, nothing new
was done to the tables for the hybrid Willcox et al. models.]

[rephrasing the question- does 20Ne count as fuel for both
the energy release and the flame speed from the table? Don seems 
to recall that we had the energy release of burning 20Ne in the 
detonation tests, which says it was included for the energy 
release. But do we just consider 12C + 12C burning for the
flame speed?]

@@

Also, the detonation tests in Willcox et al. were tests of the
energy release of the flame model and not flame speed tests. The 
model releases identical amounts of energy for both deflagrations and 
detonations in identical material, so detonation simulations were
a simple check of the modifications we made to the model to
include 20Ne in the mix.

> - Why is the MESA calculation stopped and mapped to FLASH just when
> the central temperature reaches log Tc = 8.9? What is the criterion for
> choosing such a temperature? Does it depend on composition?

Again, we did not explain our methodology well. This temperature is
very close to that required to ignite the deflagration of the
first phase of the explosion, so the progenitor is in a ready 
for ignition state. Yes, it is a (somewhat mildly) a function of 
composition, but at this temperature these models have very little 
evolution left before the flame would be born even with differing 
composition. We have updated the text (Section 2.2) to better explain 
this issue.

@@

> - Related to the last point above: it is not clear how was assigned the
> composition profile to the C+O model. In particular, why is the abundance
> of 22Ne in the C+O model smaller than that in the hybrid mixed model? Does
> it has an impact on the final yield of 56Ni?

The referee raises an interesting point about how one might perform
these parameter studies. Indeed, a more realistic C/O progenitor as
would be produced by MESA would be "state of the art." The parameterized
C/O models we chose are motivated by results from stellar evolution and,
in particular, have compositions that reflect the effect of ``simmering", 
that is slow convective burning, in the late stages of evolution as the
WD approaches the Chandrasekhar limit. This effect is observed as
the lower C fraction interior to about r =1.2e8 cm (the solid curve
in the bottom panel of Figure 1). Accordingly, while parameterized, 
the structure of C/O progenitor does reflect our current understanding 
of the state just prior to ignition.

For this study we decided to use these parameterized C-O models because
being able to construct them to match the central density and 
temperature of the hybrid models allowed us to better control the 
differences between the hybrid and traditional models. More realistic
C-O models would not match the conditions of the hybrid models, and
as we have shown in previous work, differences in density can have
a substantial effect on the yields.

We have added text to sections 2.2 and 2.4 of the manuscript and 
slightly re-arranged the description to better explain the motivation 
for our choice.

@@

Something else we could have better explained. The hybrid models in Willcox
et al have a very different structure with the highest temperature, where
ignition of the deflagration is expected, at a radius of about 300 km. 
The profiles are illustrated in Figures 2 and 9 of Willcox et al. Yet 
another thing we have made clear in the revised manuscript. In this
case, we added text to section 2.4.

> - In the first paragraph of section 3, it is argued that the yield of 56Ni
> was approximated by assuming the composition upon NSE freeze-out is 56Ni
> plus equal parts 54Fe and 58Ni. However, in many models of supernova Ia
> there is a large abundance of 56Ni in the layers that do not go beyond
> QNSE. Have you corrected for this effect somehow?

[AC: Hmmm. I think this is not right. What to say?]

The estimate of 56Ni yield does follow from assuming the NSE mix is
composed of 56Ni plus equal parts 54Fe and 58Ni, and this approach is
how all 56Ni in the simulation is calculated. 56Ni in (outer) layers
that did not go beyond QNSE would have been synthesized by fusion 
going to the Fe-group and then mixed. As such, the estimate we use 
should be robust. We have added a sentence to this paragraph of 
section 3 with citations and an additional citation to previous 
work verifying this approach in a variety of scenarios to the 
paragraph.

@@

> *General*

> - Which is the role played by the hybrid progenitors in the global plot of
> supernovae type Ia? Since the lower limit of the 56Ni mass distribution
> is 0.6 solar masses, does it mean that hybrid progenitors lead to
> normal-to-bright supernovae while C+O progenitors represent the brighter
> end of this kind of supernovae? Does it imply a dominant contribution
> of double degenerate channel for the normal supernovae Ia? Most readers
> would thank a brief discussion of these and related issues.

These are the questions that we are exploring with this and related work,
and we regret not make these clear in the introductory material. We
have added text at the end of section 1.3 addressing exactly these issues.

### 2019-10-18 paper/ms.tex
Worked in the first of Dean's suggestions.

The reaction progress variable is $\phi$ and it varies from $\phi=0$ for
unburned fuel to $\phi=1$ for burned ash. $\phi$ is evolved
via an advection-diffusion-reaction equation,
\begin{equation}
  \label{eq:ard}
  \partial_t \pv + \vec{u}\cdot\nabla \pv = \kappa \nabla^2 \pv +
\frac{1}{\tau} R\left(\phi\right) ,
\end{equation}
where $\vec{u}$ is the velocity of the fluid, $\kappa$ is the
diffusion coefficient, $\tau$ is the reaction timescale, and $R(\phi)$ is
a non-dimensional function describing the reaction. The parameters
$\kappa$, $\tau$, and $R(\phi)$ are tuned to propagate the reaction
front at a prescribed speed.  Our model uses the ``sharpened KPP''
 described by~\cite{VladWeirRyzh06},
with $R\propto(\phi-\epsilon)(1-\phi+\epsilon)$, where
$\epsilon \simeq 10^{-3}$.  This scheme has been shown to be
acoustically quiet, stable, and to give a unique flame speed
\citep{townsley.calder.ea:flame}. The input flame speeds come from
tabulated results obtained by direct numerical simulations of
thermonuclear burning.
{\color{blue}
The flame speeds are obtained via linear interpolation within a 
three-dimensional table that combines the results of \citet{timmes92} 
and \citet{Chametal08}, and the dimensions of the table are \C{12} 
mass fraction, \Ne{22} mass fraction and log of density. While the
WD contains additional species, we have shown that treating the
abundance of \Ne{22} as a proxy for neutron-rich elements captures the
speed-up of laminar flames due to neutronization and thus reasonably 
produces variations in flame speed due to composition~\citep{jacketal2010}.}
These laminar flame speeds are boosted to account for the speed-up 
of burning due to unresolved buoyancy and background turbulence~\citep{Khok95,
gamezo.khokhlov.ea:thermonuclear,townsley.calder.ea:flame,jacketal2014}.

>>>>

The reaction progress variable is $\phi$ and it varies from $\phi=0$ for
unburned fuel to $\phi=1$ for burned ash. $\phi$ is evolved
via an advection-diffusion-reaction equation,
\begin{equation}
  \label{eq:ard}
  \partial_t \pv + \vec{u}\cdot\nabla \pv = \kappa \nabla^2 \pv +
\frac{1}{\tau} R\left(\phi\right) ,
\end{equation}
where $\vec{u}$ is the velocity of the fluid, $\kappa$ is the
diffusion coefficient, $\tau$ is the reaction timescale, and $R(\phi)$ is
a non-dimensional function describing the reaction. The parameters
$\kappa$, $\tau$, and $R(\phi)$ are tuned to propagate the reaction
front at a prescribed speed.  Our model uses the ``sharpened KPP''
 described by~\cite{VladWeirRyzh06},
with $R\propto(\phi-\epsilon)(1-\phi+\epsilon)$, where
$\epsilon \simeq 10^{-3}$.  This scheme has been shown to be
acoustically quiet, stable, and to give a unique flame speed
\citep{townsley.calder.ea:flame}. The input flame speeds come from
tabulated results obtained by direct numerical simulations of
thermonuclear burning.
{\color{blue}
The flame speeds are obtained via linear interpolation within a 
three-dimensional table that combines the results of \citet{timmes92} 
and \citet{Chametal08}, and the dimensions of the table are \C{12} 
mass fraction, \Ne{22} mass fraction and log of density. While the
WD contains additional species, we have shown that treating the
abundance of \Ne{22} as a proxy for neutron-rich elements captures the
speed-up of laminar flames due to neutronization and thus reasonably 
produces variations in flame speed due to composition~\citep{jacketal2010}.}
{\color{green} Using these tables, which were made for mixtures without $^{20}$Ne,
effectively assumes that the substitution of $^{20}$Ne for $^{16}$O will not
change the flame speeds significantly.  We consider this a reasonable
approximation given that, in the interior of our star, $^{16}$O is still much
more abundant than $^{20}$Ne, and that the flame propagation is largely
dominated by turbulent effects.}
These laminar flame speeds are boosted to account for the speed-up 
of burning due to unresolved buoyancy and background turbulence~\citep{Khok95,
gamezo.khokhlov.ea:thermonuclear,townsley.calder.ea:flame,jacketal2014}.
